Sound and Automated Synthesis of Digital Stabilizing Controllers for Continuous Plants \thanks{Supported by EPSRC grant EP/J012564/1 and ERC project 280053 (CPROVER).}

### 2017-02-01 hscc2017/paper.tex
wording

The fifth set of benchmarks contains the \textit{DC Motor Rate} discrete model $G_{5}(z)$, which 
describes the angular velocity of a DC Motor plant~\cite{Franklin15}. 
%
%\begin{equation}
%\label{DC-Motor-Rate}
%G_{5}(z)=\frac{ 0.1898z + 1.8027\times{10^{-4}}}{1.0z^{2} -0.9012z -1.0006\times{10^{-16}}}. \nonumber
%\end{equation}
%
The sixth set of benchmarks contains the \textit{Helicopter Longitudinal Motion} discrete model $G_{6}(z)$,
which provides the longitudinal motion dynamics of a helicopter plant~\cite{Franklin15}. 
%
%\begin{equation}
%\label{Helicopter-Longitudinal-Motion}
%G_{6}(z)=\frac{15.1315z^{2} + 17.8600z + 17.4549}{z^{3} -2.6207z^{2} + 2.3586z -0.6570}. \nonumber
%\end{equation}
%
The seventh set of benchmarks contains the \textit{Inverted Pendulum} discrete model $G_{7}(z)$, which 
describes a pendulum dynamics with its center of mass above its pivot point~\cite{Franklin15}. 
%
%\begin{equation}
%\label{Inverted-Pendulum}
%G_{7}(z)=\frac{0.0263z^{2} + 0.0143z -0.0383}{z^{4} -4.2553z^{3} + 6.5105z^{2} -4.2553z + 1}. \nonumber
%\end{equation}
%
The eighth set of benchmarks contains the \textit{Magnetic Suspension} discrete model $G_{8}(z)$, which describes the dynamics of a mass that levitates with support only of a magnetic field~\cite{Franklin15}. 
%
%\begin{equation}
%\label{Magnetic-Suspension}
%G_{8}(z)=\frac{6.769\times{10^{13}}z + 6.784\times{10^{13}}}{z^{2} -5.415\times{10^{13}}z + 4.23\times{10^{11}}}. \nonumber
%\end{equation}

The ninth set of benchmarks contains the \textit{1/4 Car Suspension} discrete model $G_{9}(z)$,
which represents the dynamics of a single wheel suspension plant, {\it i.e.}, a system that connects a car to a wheel and allows relative motion between both parts~\cite{Franklin15}.
%
%\begin{equation}
%\label{Car-Suspension}
%G_{8}(z)=\frac{0.25z^{3} + 0.5z^{3} + 0.25z -5.7065\times{10^{-10}}}{z^{3} + 6.8455\times{10^{-9}}z^{2} + 3.3925\times{10^{-17}}z - 3.4667\times%{10^{-94}}}. \nonumber
%\end{equation}
%
The tenth set of benchmarks contains the \textit{Computer Tape Driver} discrete model $G_{10}(z)$, which 
describes a system to read and write data on a storage device in the computer~\cite{Franklin15}.
%
%\begin{equation}
%\label{Computer-Tape-Driver}
%G_{10}(z)=\frac{0.0200z -3.8303\times{10^{-176}}}{1.0z -4.6764\times{10^{-166}}}. \nonumber
%\end{equation}
The eleventh benchmark describe the discrete model of a DC servo motor velocity dynamics~\cite{exampleCAD,Tan01}.

>>>>

The fifth set of benchmarks contains the \textit{DC Motor Rate} discrete model $G_{5}(z)$, which 
describes the angular velocity of a DC Motor plant~\cite{Franklin15}. 
%
%\begin{equation}
%\label{DC-Motor-Rate}
%G_{5}(z)=\frac{ 0.1898z + 1.8027\times{10^{-4}}}{1.0z^{2} -0.9012z -1.0006\times{10^{-16}}}. \nonumber
%\end{equation}
%
The sixth set of benchmarks contains the \textit{Helicopter Longitudinal Motion} discrete model $G_{6}(z)$,
which provides the longitudinal motion dynamics of a helicopter~\cite{Franklin15}. 
%
%\begin{equation}
%\label{Helicopter-Longitudinal-Motion}
%G_{6}(z)=\frac{15.1315z^{2} + 17.8600z + 17.4549}{z^{3} -2.6207z^{2} + 2.3586z -0.6570}. \nonumber
%\end{equation}
%
The seventh set of benchmarks contains the \textit{Inverted Pendulum} discrete model $G_{7}(z)$, which 
describes a pendulum dynamics with its center of mass above its pivot point~\cite{Franklin15}. 
%
%\begin{equation}
%\label{Inverted-Pendulum}
%G_{7}(z)=\frac{0.0263z^{2} + 0.0143z -0.0383}{z^{4} -4.2553z^{3} + 6.5105z^{2} -4.2553z + 1}. \nonumber
%\end{equation}
%
The eighth set of benchmarks contains the \textit{Magnetic Suspension} discrete model $G_{8}(z)$, which describes the dynamics of a mass that levitates with support only of a magnetic field~\cite{Franklin15}. 
%
%\begin{equation}
%\label{Magnetic-Suspension}
%G_{8}(z)=\frac{6.769\times{10^{13}}z + 6.784\times{10^{13}}}{z^{2} -5.415\times{10^{13}}z + 4.23\times{10^{11}}}. \nonumber
%\end{equation}

The ninth set of benchmarks contains the \textit{1/4 Car Suspension} discrete model $G_{9}(z)$,
which represents the dynamics of a single wheel suspension plant, {\it i.e.}, a system that connects a car to a wheel and allows relative motion between both parts~\cite{Franklin15}.
%
%\begin{equation}
%\label{Car-Suspension}
%G_{8}(z)=\frac{0.25z^{3} + 0.5z^{3} + 0.25z -5.7065\times{10^{-10}}}{z^{3} + 6.8455\times{10^{-9}}z^{2} + 3.3925\times{10^{-17}}z - 3.4667\times%{10^{-94}}}. \nonumber
%\end{equation}
%
The tenth set of benchmarks contains the \textit{Computer Tape Driver} discrete model $G_{10}(z)$, which 
describes a system to read and write data on a storage device~\cite{Franklin15}.
%
%\begin{equation}
%\label{Computer-Tape-Driver}
%G_{10}(z)=\frac{0.0200z -3.8303\times{10^{-176}}}{1.0z -4.6764\times{10^{-166}}}. \nonumber
%\end{equation}
The eleventh benchmark describe the discrete model of a DC servo motor velocity dynamics~\cite{exampleCAD,Tan01}.
